### 2019-07-11 papers/journal/bio.tex
Added reference to the Appendix fig
Updated the rebuttal

%We assume that for fusion to occur, the pair of SNARE types involved on the vesicle and compartment must both be in an active state. Whether these SNAREs are active or inactive depends on the other molecules found on the vesicle or compartment, respectively. We test many different versions of this kind of molecular regulation. Most generally, the activity state of a given SNARE can be a Boolean function of all the molecular types on a compartment or vesicle. We have also tested \cite{shukla} a particularly simple regulation mechanism in which two SNAREs that can pair to drive fusion inhibit one another; this is the \textit{pairing inhibition}. This is motivated by the idea that pairing must generate an inactive bi-molecular complex.

@@

%\ankit{We need not specify Synthesis here. Only connectivity use next subsection to build this.}
%\somya{But this is the para where we explain why connectivity is interesting an biological property}
%\ankit{Yes; Both of our remark looks correct!}
%The vesicle transport graphs available today for eukaryotic organisms are incomplete themselves. 
%%
%In this situation, we use our result as a tool to predict missing edges which satisfy the graph connectivity constraint. 
%%
%These predictions are intended to be used as guides for future experiments. 
%%
%A mismatch between our predictions and experiments would indicate that our current understanding of the VTS molecules is necessarily incomplete. 
%%
%Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is complete.\\
%%
%\begin{table}[!t]
%	\caption{Table Caption}
%	\label{tab1}
%	\centering
%	{\setlength\tabcolsep{0.1pt}%
%		\begin{tabular}{ccccccccccccccc}
%			& $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ && & $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ \\
%			$D_1$ & & \cca{0} & \cca{0} & \cca{0} & \cca{2} & \cca{0} && $D_1$ && \cca{0} & \cca{0} & \cca{2} & \cca{2} & \cca{2} \\
%			$D_2$ & \cca{0} & & \cca{2} & \cca{0} & \cca{2} & \cca{0} && $D_2$ & \cca{0} &  & \cca{3} & \cca{0} & \cca{0} & \cca{2} \\
%			$D_3$ & \cca{7} & \cca{4} &  & \cca{3} & \cca{0} & \cca{4} && $D_3$ & \cca{0} & \cca{4} &  & \cca{4} & \cca{2} & \cca{0} \\
%			$D_4$ & \cca{3} & \cca{0} & \cca{7} &  & \cca{4} & \cca{0} && $D_4$ & \cca{0} & \cca{0} & \cca{5} &  & \cca{0} & \cca{0} \\
%			$D_5$ & \cca{3} & \cca{7} & \cca{7} & \cca{2} &  & \cca{4} && $D_5$ & \cca{2} & \cca{2} & \cca{0} & \cca{4} &  & \cca{4} \\
%			$D_6$ & \cca{2} & \cca{2} & \cca{7} & \cca{2} & \cca{6} &  && $D_6$ & \cca{2} & \cca{2} & \cca{3} & \cca{0} & \cca{4} & \\
%	\end{tabular}}
%\end{table}
%
\input{fig2}
%
\begin{example}
%
In Fig.~\ref{fig:M1}, we present a VTS that has 2 compartments and 18 molecules with its corresponding pairing matrix.
%
%Molecules are represented as $Q_{i}$'s or $R_{i}$'s to make a clear distinction between Q and R SNAREs.
%
In the VTS, labels are a set of molecule, where we show active molecules in red color.
%
The activity of the molecules on the node is controlled
by the presence of the other molecules (exact Boolean function is not shown). 
%
The activity of the molecules on an edge is determined by the corresponding pairing matrix.
%
Note that molecules $X$ and $Y$ do not take part in the fusion but determine the activity of molecules at the corresponding nodes.
%
Below the VTS, we show the pairing matrix.
%
Rows in the matrix correspond to the labels of edges, and columns correspond to the labels of nodes.
%
An entry 1 represents pairing between molecules and 0 represents no pairing.
%
Every molecule flows on a cycle, ensuring steady state.
%
This is a 4-connected graph.
\end{example}
\input{fig3}
\begin{example}
	In Fig.~\ref{fig:synth-vts1}, we present a partial input VTS that has 3 compartments. Fig.~\ref{fig:synth-vts2} present it's complete output VTS. Every molecule present on the node is active. The activity of the molecules on an edge is determined by the presence of the other molecules. Each label represent particular type of molecule. The synthesis is performed against the stability and 3-connectivity. Synthesized edge is in red color and synthesized molecules are presented in blue. The synthesis adds one edge and 7 molecules to complete the partial VTS. For the sake of clarity, we have not presented the activity of molecules, the corresponding pairing matrix and remaining molecules on the nodes. 
	%The presented graph is a subgraph of a VTS discussed in details in appendix.
\end{example}

>>>>

In this work, we use the term activity to have very specific scope; it only implies the ability to cause membrane fusion and it only applies to SNAREs. 
%
In this sense, it indeed does not matter whether the molecule interacting with the SNARE is active or not. 
%
For example, Qa-SNAREs are only active on target compartments (regulation by SM proteins achieves this \cite{baker2016chaperoning}), but when present on vesicles with its other cognate SNAREs, it nevertheless will participate in SNARE complex formation within the same vesicle membrane, and thus inhibit its SNARE partners from causing vesicle fusion.
%We assume that for fusion to occur, the pair of SNARE types involved on the vesicle and compartment must both be in an active state. Whether these SNAREs are active or inactive depends on the other molecules found on the vesicle or compartment, respectively. We test many different versions of this kind of molecular regulation. Most generally, the activity state of a given SNARE can be a Boolean function of all the molecular types on a compartment or vesicle. We have also tested \cite{shukla} a particularly simple regulation mechanism in which two SNAREs that can pair to drive fusion inhibit one another; this is the \textit{pairing inhibition}. This is motivated by the idea that pairing must generate an inactive bi-molecular complex.

@@

%\ankit{We need not specify Synthesis here. Only connectivity use next subsection to build this.}
%\somya{But this is the para where we explain why connectivity is interesting an biological property}
%\ankit{Yes; Both of our remark looks correct!}
%The vesicle transport graphs available today for eukaryotic organisms are incomplete themselves. 
%%
%In this situation, we use our result as a tool to predict missing edges which satisfy the graph connectivity constraint. 
%%
%These predictions are intended to be used as guides for future experiments. 
%%
%A mismatch between our predictions and experiments would indicate that our current understanding of the VTS molecules is necessarily incomplete. 
%%
%Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is complete.\\
%%
%\begin{table}[!t]
%	\caption{Table Caption}
%	\label{tab1}
%	\centering
%	{\setlength\tabcolsep{0.1pt}%
%		\begin{tabular}{ccccccccccccccc}
%			& $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ && & $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ \\
%			$D_1$ & & \cca{0} & \cca{0} & \cca{0} & \cca{2} & \cca{0} && $D_1$ && \cca{0} & \cca{0} & \cca{2} & \cca{2} & \cca{2} \\
%			$D_2$ & \cca{0} & & \cca{2} & \cca{0} & \cca{2} & \cca{0} && $D_2$ & \cca{0} &  & \cca{3} & \cca{0} & \cca{0} & \cca{2} \\
%			$D_3$ & \cca{7} & \cca{4} &  & \cca{3} & \cca{0} & \cca{4} && $D_3$ & \cca{0} & \cca{4} &  & \cca{4} & \cca{2} & \cca{0} \\
%			$D_4$ & \cca{3} & \cca{0} & \cca{7} &  & \cca{4} & \cca{0} && $D_4$ & \cca{0} & \cca{0} & \cca{5} &  & \cca{0} & \cca{0} \\
%			$D_5$ & \cca{3} & \cca{7} & \cca{7} & \cca{2} &  & \cca{4} && $D_5$ & \cca{2} & \cca{2} & \cca{0} & \cca{4} &  & \cca{4} \\
%			$D_6$ & \cca{2} & \cca{2} & \cca{7} & \cca{2} & \cca{6} &  && $D_6$ & \cca{2} & \cca{2} & \cca{3} & \cca{0} & \cca{4} & \\
%	\end{tabular}}
%\end{table}
%
\input{fig2}
%
\begin{example}
%
In Fig.~\ref{fig:M1}, we present a VTS that has 2 compartments and 18 molecules with its corresponding pairing matrix.
%
%Molecules are represented as $Q_{i}$'s or $R_{i}$'s to make a clear distinction between Q and R SNAREs.
%
In the VTS, labels are a set of molecule, where we show active molecules in red color.
%
The activity of the molecules on the node is controlled
by the presence of the other molecules (exact Boolean function is not shown). 
%
The activity of the molecules on an edge is determined by the corresponding pairing matrix.
%
Note that molecules $X$ and $Y$ do not take part in the fusion but determine the activity of molecules at the corresponding nodes.
%
Below the VTS, we show the pairing matrix.
%
Rows in the matrix correspond to the labels of edges, and columns correspond to the labels of nodes.
%
An entry 1 represents pairing between molecules and 0 represents no pairing.
%
Every molecule flows on a cycle, ensuring steady state.
%
This is a 4-connected graph.
\end{example}
\input{fig3}
\begin{example}
	In Fig.~\ref{fig:synth-vts1}, we present a partial input VTS that has 3 compartments. Fig.~\ref{fig:synth-vts2} present it's complete output VTS. Every molecule present on the node is active. The activity of the molecules on an edge is determined by the presence of the other molecules. Each label represent particular type of molecule. The synthesis is performed against the stability and 3-connectivity. Synthesized edge is in red color and synthesized molecules are presented in blue. The synthesis adds one edge and 7 molecules to complete the partial VTS. For the sake of clarity, we have not presented the activity of molecules, the corresponding pairing matrix and remaining molecules on the nodes. This synthetic example is a sub-graph of the VTS shown in the \ref{fig:mukund-vts}. Please refer to \ref{sec:ex-vts} for complete detail. 
	%The presented graph is a subgraph of a VTS discussed in details in appendix.
\end{example}

### 2019-07-11 papers/journal/conclusion.tex
Updated the rebuttal

\noindent 
We demonstrate in our work how local regulatory interactions between molecules of the VTS, translate
into a global, observable properties of the VTS. 
%
Interactions between SNARE proteins and their
regulators, which in its simplest form can be encoded in a pairing matrix, constrain the topological
properties of the transport graph; all VTSs based on V-SNARE T-SNARE interactions must be 2-strongly connected.
% 
Additionally, we demonstrate how we can aid in predicting new vesicles given an incomplete VTS as input. 
%
Our approach demonstrates the power of SMT solvers in a novel application and the value of careful encoding of the problems into SMT queries. 
%
We manage to scale the tool up
to the size that makes the tool biologically relevant.
%To conclude, we have established a connection between vesicle transport graph connectedness and underlying rules of SNARE pairing and regulation. 
%%
%The constraints implied by SNARE protein properties translates into
%mathematically elegant properties of the transport graph, namely its connectivity.
%%
%Our approach demonstrates the power of SMT solvers in a {\em novel} application and the value of careful encoding of the problems into SMT queries. 
%We manage to scale the tool up to the size that makes the tool biologically relevant.
%

However, the problem of searching for all $k$-connected VTSs induces quantifier alternation in the encodings.
%
Therefore, a simple call to SAT solver may not work efficiently. 
%
We used QBF solvers for such queries.
%
Our connectivity results contain many predictions which can in principle be tested through cell-biological experiments. 
%
One may also be interested in counting the number of graphs that satisfy
a given property. 
%
Exact counting of the graphs using SAT solvers may prove to be very
difficult. 
%
We are planning to employ approximate counting methods for finding the solution.
%

>>>>

\noindent 
We demonstrate in our work how local regulatory interactions between molecules of the VTS, translate into a global, observable properties of the VTS. 
%
Interactions between SNARE proteins and their regulators, which in its simplest form can be encoded in a pairing matrix, constrain the topological properties of the transport graph; all VTSs based on SNARE protein interactions must be 2-strongly connected. 
%
Additionally, we demonstrate how we can aid in predicting new vesicles given an incomplete VTS as input. 
%
Our approach demonstrates the power of SMT solvers in a novel application and the value of careful encoding of the problems into SMT queries. 
%
We manage to scale the tool up to the size that makes the tool biologically relevant.
%
%To conclude, we have established a connection between vesicle transport graph connectedness and underlying rules of SNARE pairing and regulation. 
%%
%The constraints implied by SNARE protein properties translates into
%mathematically elegant properties of the transport graph, namely its connectivity.
%%
%Our approach demonstrates the power of SMT solvers in a {\em novel} application and the value of careful encoding of the problems into SMT queries. 
%We manage to scale the tool up to the size that makes the tool biologically relevant.
%

However, the problem of searching for all $k$-connected VTSs induces quantifier alternation in the encodings. 
%
Therefore, a simple call to SAT solver may not work efficiently. 
%
We used QBF solvers for such queries. Our connectivity results contain many predictions which can in principle be tested through cell-biological experiments. 
%
For any input VTS, our tool outputs multiple possible solutions in the form of predictions of undiscovered vesicles and cargo molecules on specific vesicles. 
%
Such predictions could be used to guide biological experiments. Since a VTS that is close to completion is expected to have fewer alternative solutions to test, we expect that testing the predictions of our tool would become more tractable as more and more vesicles are discovered. 
%
One may also be interested in counting the number of graphs that satisfy a given property. 
%
Exact counting of the graphs using SAT solvers may prove to be very difficult. We are planning to employ approximate counting methods for finding the solution.
